---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE, message=FALSE, results='hide'}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-",
  echo = TRUE,
  fig.width = 8,
  fig.height = 6
)

```

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/trendeval)](https://CRAN.R-project.org/package=trendeval)
[![Codecov test coverage](https://codecov.io/gh/reconverse/trendeval/branch/master/graph/badge.svg)](https://codecov.io/gh/reconverse/trendeval?branch=master)
[![R build status](https://github.com/reconverse/trendeval/workflows/R-CMD-check/badge.svg)](https://github.com/reconverse/trendeval/actions)
<!-- badges: end -->


# Trendeval

*trendeval* aims to provide a coherent interface for evaluating models fit with
the [trending](https://github.com/reconverse/trending) package. Whilst it
is useful in an interactive context, it's main focus is to provide an intuitive
interface on which other packages can be developed 
(e.g. [*trendbreaker*](https://github.com/reconhub/trendbreaker)).

## Installing the package

You can install the stable version of this package from
[CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
install.packages("trendeval")
```

The development version can be installed from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
if (!require(remotes)) {
  install.packages("remotes")
}
remotes::install_github("reconverse/trendeval", build_vignettes = TRUE)
```

## Model selection example
```{r, message = FALSE}
library(dplyr)      # for data manipulation
library(outbreaks)  # for data
library(trending)   # for trend fitting
library(trendeval)  # for model selection

# load data
data(covid19_england_nhscalls_2020)

# define a selection of model in a named list
models  <- list(
  simple = lm_model(count ~ day),
  glm_poisson = glm_model(count ~ day, family = "poisson"),
  glm_poisson_weekday = glm_model(count ~ day + weekday, family = "quasipoisson"),
  glm_quasipoisson = glm_model(count ~ day, family = "poisson"),
  glm_quasipoisson_weekday = glm_model(count ~ day + weekday, family = "quasipoisson"),
  glm_negbin = glm_nb_model(count ~ day),
  glm_negbin_weekday = glm_nb_model(count ~ day + weekday),
  will_error = glm_nb_model(count ~ day + nonexistant)
)

# select 8 weeks of data (from a period when the prevalence was decreasing)
last_date <- as.Date("2020-05-28")
first_date <- last_date - 8*7
pathways_recent <-
  covid19_england_nhscalls_2020 %>%
  filter(date >= first_date, date <= last_date) %>%
  group_by(date, day, weekday) %>%
  summarise(count = sum(count), .groups = "drop")

# split data for fitting and prediction
dat <-
  pathways_recent %>%
  group_by(date <= first_date + 6*7) %>%
  group_split()
fitting_data <- dat[[2]]
pred_data <- select(dat[[1]], date, day, weekday)

# assess the models using the evaluate_resampling
results <- 
  models %>% 
  evaluate_resampling(fitting_data, metric = "rmse") %>% 
  summary
results
```

### Example of how this output could then be used
```{r}
library(tidyr)      # for data manipulation
library(purrr)      # for data manipulation
library(ggplot2)    # for plotting

# Pull out the model with the lowest RMSE
best_by_rmse <- 
  results %>% 
  slice_min(value) %>% 
  select(model_name) %>% 
  pluck(1,1) %>% 
  pluck(models, .)

# Now let's look at the following 14 days as well
new_dat <-
  covid19_england_nhscalls_2020 %>% 
  filter(date > "2020-05-28", date <= "2020-06-11") %>% 
  group_by(date, day, weekday) %>%
  summarise(count = sum(count), .groups = "drop")

all_dat <- bind_rows(pathways_recent, new_dat)

out <- 
  best_by_rmse %>%  
  fit(pathways_recent) %>% 
  predict(all_dat) %>%  
  pluck(1)
out

# plot output
ggplot(out, aes(x = date, y = count)) +
  geom_line() +
  geom_ribbon(mapping = aes(x = date, ymin = lower_ci, ymax = upper_ci),
              data = out, alpha = 0.5, fill = "#BBB67E") +
  geom_ribbon(mapping = aes(x = date, ymin = lower_pi, ymax = upper_pi),
              data = out, alpha = 0.5, fill = "#BBB67E") +
  geom_vline(xintercept = as.Date("2020-05-28") + 0.5) +
  theme_bw()
```

# Resources

## Getting help online

Bug reports and feature requests should be posted on *github* using the 
[*issue* system](https://github.com/reconverse/trendeval/issues). All other
questions should be posted on the **RECON** slack channel see
<https://www.repidemicsconsortium.org/forum/> for details on how to join.
  
