---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE, message=FALSE, results='hide'}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-",
  echo = TRUE,
  fig.width = 8,
  fig.height = 6
)

```

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/trendeval)](https://CRAN.R-project.org/package=trendeval)
[![Codecov test coverage](https://codecov.io/gh/reconverse/trendeval/branch/master/graph/badge.svg)](https://codecov.io/gh/reconverse/trendeval?branch=master)
[![R build status](https://github.com/reconverse/trendeval/workflows/R-CMD-check/badge.svg)](https://github.com/reconverse/trendeval/actions)
<!-- badges: end -->


# Trendeval

*trendeval* aims to provide a coherent interface for evaluating models fit with
the [trending](https://github.com/reconverse/trending) package. Whilst it
is useful in an interactive context, it's main focus is to provide an intuitive
interface on which other packages can be developed 
(e.g. [*trendbreaker*](https://github.com/reconhub/trendbreaker)).

## Installing the package

You can install the stable version of this package from
[CRAN](https://CRAN.R-project.org) with:

```{r, eval=FALSE}
install.packages("trendeval")
```

The development version can be installed from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
if (!require(remotes)) {
  install.packages("remotes")
}
remotes::install_github("reconverse/trendeval", build_vignettes = TRUE)
```

# Resources

## Getting help online

Bug reports and feature requests should be posted on *github* using the 
[*issue* system](https://github.com/reconverse/trendeval/issues). All other
questions should be posted on the **RECON** slack channel see
<https://www.repidemicsconsortium.org/forum/> for details on how to join.
  
