---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, echo = FALSE, message=FALSE, results='hide'}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-",
  echo = TRUE,
  fig.width = 8,
  fig.height = 6
)

```

<!-- badges: start -->
[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/trendeval)](https://CRAN.R-project.org/package=trendeval)
[![Codecov test coverage](https://codecov.io/gh/reconhub/trendeval/branch/master/graph/badge.svg)](https://codecov.io/gh/reconhub/trendeval?branch=master)
[![R build status](https://github.com/reconhub/trendeval/workflows/R-CMD-check/badge.svg)](https://github.com/reconhub/trendeval/actions)
<!-- badges: end -->

<br>
**<span style="color: red;">Disclaimer</span>**

This package is a work in progress. Please reach out to the
authors before using.

# Trendeval

*trendeval* aims to provide a coherent interface for evaluating models fit with
the [trending](https://github.com/reconhub/trending) package. Whilst it
is useful in an interactive context, it's main focus is to provide an intuitive
interface on which other packages can be developed 
(e.g. [*trendbreaker*](https://github.com/reconhub/trendbreaker)).

## Installing the package

Once it is released on [CRAN](https://CRAN.R-project.org), you will be able to
install the stable version of the package with:

```{r, eval=FALSE}
install.packages("trendeval")
```

The development version can be installed from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
if (!require(remotes)) {
  install.packages("remotes")
}
remotes::install_github("reconhub/trendeval", build_vignettes = TRUE)
```

## Model selection example
```{r}
library(dplyr)      # for data manipulation
library(outbreaks)  # for data
library(trending)   # for trend fitting
library(trendeval)  # for model selection

# load data
data(covid19_england_nhscalls_2020)

# define a model
models  <- list(
  simple = lm_model(count ~ day),
  glm_poisson = glm_model(count ~ day, family = "poisson"),
  glm_negbin = glm_nb_model(count ~ day + weekday),
  will_error = glm_nb_model(count ~ day + nonexistant)
)

# select 6 weeks of data (from a period when the prevalence was decreasing)
last_date <- as.Date("2020-05-28")
first_date <- last_date - 8*7
pathways_recent <-
  covid19_england_nhscalls_2020 %>%
  filter(date >= first_date, date <= last_date) %>%
  group_by(date, day, weekday) %>%
  summarise(count = sum(count), .groups = "drop")

# split data for fitting and prediction
dat <-
  pathways_recent %>%
  group_by(date <= first_date + 6*7) %>%
  group_split()
fitting_data <- dat[[2]]
pred_data <- select(dat[[1]], date, day, weekday)


out <- capture.output( # no log output in readme :)
  auto_select <- select_model(fitting_data, models,
    method = evaluate_resampling,
    metrics = list(yardstick::rmse, yardstick::huber_loss, yardstick::mae)
  )
)

auto_select$leaderboard

```

# Resources

## Getting help online

Bug reports and feature requests should be posted on *github* using the 
[*issue* system](https://github.com/reconhub/incidence2/issues). All other
questions should be posted on the **RECON** slack channel see
<https://www.repidemicsconsortium.org/forum/> for details on how to join.
  
